Improving the Fidelity of Redox Flow Battery Schedule Optimisation for more Accurate Techno-economic Analyses.

### 2018-11-19 Paper/main.tex
Update main.tex

Both the LP and NLP solutions involve charging the VRFB when the electrical price is low (e.g. 05:00 to 07:00) and discharging it when the price is high (e.g. 10:00 to 13:00). The LP optimal profile involves discharging or charging the system at high current-density in the four hours with the most extreme prices. The NLP optimal schedule also targets the most extreme periods, but spreads the charging/discharging out. This is the consequence of factoring variable ohmic losses in the objective function, where high current-density is penalised by higher losses. Under the LP formulation, the VRFB is predicted to generate \pounds 0.068, whereas the NLP formulation predicts a revenue of \pounds 0.063. In reality however, the voltaic losses that would occur under the LP schedule would reduce the revenue to \pounds 0.051. Across 2017, LP scheduling would have resulted in \pounds \SI{22.61}{\per\kilo\watt}, against a prediction of \pounds \SI{33.16}{\per\kilo\watt}, and NLP scheduling would have yielded \pounds \SI{27.99}{\per\kilo\watt}.

>>>>

Both the LP and NLP solutions involve charging the VRFB when the electrical price is low (e.g. 05:00 to 07:00) and discharging it when the price is high (e.g. 10:00 to 13:00). The LP optimal profile involves discharging or charging the system at high current-density in the four hours with the most extreme prices. The NLP optimal schedule also targets the most extreme periods, but spreads the charging/discharging out. This is the consequence of factoring variable ohmic losses in the objective function, where high current-density is penalised by higher losses. Under the LP formulation, the VRFB is predicted to generate \pounds \SI{0.068}{\per\kilo\watt}, whereas the NLP formulation predicts a revenue of \pounds \SI{0.063}{\per\kilo\watt}. In reality however, the voltaic losses that would occur under the LP schedule would reduce the revenue to \pounds 0.051. Across 2017, LP scheduling would have resulted in \pounds \SI{22.61}{\per\kilo\watt}, against a prediction of \pounds \SI{33.16}{\per\kilo\watt}, and NLP scheduling would have yielded \pounds \SI{27.99}{\per\kilo\watt}.
